---
title: "Tables to Explore Individual Cases"
output:
  html_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 7
    highlight: tango
    theme: readable
  pdf_document:
    fig_caption: yes
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir="..")
```

```{r, include=FALSE}
library(knitr)
library(kableExtra)
load("./01_outputdata/eac_cross-section_and_polygons.RData")
```

## Municipalities Receiving Aid with Positive Trend
```{r aid-trend-df, include=FALSE}
pos_trend_aid <- spdf_eac_df %>%
  group_by(codmuni
  ) %>%
  summarise_all(first
  ) %>%
  filter(trendcropveg_cat == "Positive Trend" & muni_locd == 1
  ) %>%
  dplyr::select(codane = codmuni,
         department,
         municipality,
         trend_cropveg = trendcropveg,
         state_exposure = vio_31_mean,
         guerilla_exposure = vio_32_mean,
         coca_yrs_avg = vio_13,
         coca_in_2013 = illegal_crops,
         conflict_incidence = vio_46,
         state_guer_dispute = vio_34_mean,
         trend_direction = trendcropveg_cat,
         aid_given = muni_locd
  ) %>%
  arrange(department, municipality)
```

```{r aid-trend-table}
pos_trend_aid %>%
  kable("html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 8)
```
## Variable Descriptions
*trend_cropveg* = positive trend/growth in MODIS Cropland/Natural Vegetation Cover (hectares)

*state_exposure* = proportion of years in which municipality population comes in contact with govt forces

*guerilla_exposure* = proportion of years in which municipality population comes in contact with guerilla forces

*coca_yrs_avg* = proportion of years in which municipality contains coca growth

*conflict_incidence* = 1-5 index of conflict intensity. Moving from low to high incidence

*state_guer_dispute* = proportion of years with govt and guerilla force conflict

*state_guer_dispute* = proportion of years with govt and guerilla force conflict





